\documentclass{article}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{enumerate}
\usepackage{setspace}
\usepackage{sectsty}
\usepackage{soul,xcolor}
\usepackage{fancyhdr}
\usepackage[tocindentauto]{tocstyle}

\renewcommand{\thesection}{\Roman{section}}
\renewcommand \thesubsection{\roman{subsection}}

\newenvironment{li}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{enumerate}}

\begin{document}
% set strikethrough color to red
\setstcolor{red}

\Large{Davis Computer Science Club Bylaws}
\normalsize{}
\tableofcontents
\newpage

\singlespacing
\sectionfont{\Large}
\subsectionfont{\large}

\section{Davis Computer Science Club}
\subsection{Name}
The name of this organization shall be the Davis Computer Science Club, hereinafter referred to as the CS Club, Davis CS Club, or the CS Club @ UC Davis.

\subsection{Purpose}
The purpose of the Davis CS Club shall be:
\begin{li}
\item To organize and connect UC Davis students interested in the field of Computer Science.
\item To cultivate a professional development of its members.
\item To present new and engaging opportunities in novel applications of Computer Science.
\item To promote faculty-student relations in the Computer Science Department.
\item To pioneer students into leadership positions.
\item To provide sustainable funding to support all of these purposes.
\end{li}

\subsection{Actions}
The Davis CS Club shall fulfill its purpose with these actions including, but not limited to the following:
\begin{li}
\item Represent the interests of its members through Core Officers.
\item Allocate the annual budget and oversee the maintenance of all Budgetary Reserves in the manner it deems as the best interests of the club.
\item Take official stances and undertake projects and actions on issues that are of importance to the club, its members, and is within constraints of our stated purpose.
\end{li}

\subsection{Duties and Responsibilities}
The Davis CS Club shall:
\begin{li}
\item Perform all duties and responsibilities as specified in the Davis Computer Science Club Bylaws.
\item Hold meetings in accordance with the Davis CS Club Bylaws.
\item Publicize and communicate the Actions of the club to the appropriate student body.
\item Oversee all Actions and programs promoted and/or sponsored (funded) by the Davis CS Club.
\item Oversee, maintain, and regulate all Davis CS Club property, assets, and funds.
\item Ensure appropriate membership to the Core Officers and all its committees as provided for in these bylaws, as it sees fit.
\end{li}

% ////////////////////////////////////////////////
% ////////////////////////////////////////////////

\section{Members}
The Davis CS Club shall consist of the following:
\begin{li}
\item Core Officers
\item Committee Members
\item Regular Members
\item Club Advisor
% \item Club Consultant
% 	The Club Consultant shall be responsible for the following:
% 	\begin{li}
% 	\item Overseer internal affairs regarding 
% 	\end{li}
\end{li}

\subsection{Eligibility Requirements}
For voting privileges, every continuing member of the Davis Computer Science Club must:
\begin{li}
\item Be a current University of California, Davis student.
\item Have attended at least two (2) meetings per quarter.
\end{li}

\noindent A non-voting member of the Davis CS Club may be any of the following:
\begin{li}
\item A current University of California, Davis student.
\item A University of California, Davis alumni.
\item A University of California, Davis affiliate.
\end{li}

\noindent Every Core Officer and Committee Member must be a voting member.

\subsection{Duties and Responsibilities}
Each Davis CS Club Committee member shall:
\begin{li}
\item Serve as a member of at least one (1) Davis CS Club Committee.
\item Attend a minimum of three (3) meetings and one (1) event per quarter.
\end{li}

\noindent The Club Advisor shall be a lecturer or a professor from the Computer Science Department in the University of California, Davis, and shall be responsible for the following:
	\begin{li}
	\item Promote student-faculty relations.
	\item Be available to meet or communicate with Officers regarding any club activities at the advisor's convenience.
	% add a section about changing club advisors.
	\end{li}

\subsection{Resignation}
\begin{li}
\item Any member may resign from the club at any time by submitting a resignation in writing to any Core Officers.
\item Verbal resignations shall be considered official and binding only when made at a Davis CS Club meeting.
\item Resignations are immediately effective unless a date is otherwise specified.
\end{li}

% ////////////////////////////////////////////////
% ////////////////////////////////////////////////

\section{Officers}
The collective body of the Davis CS Club Core Officers shall be alternatively referred to as the Core Body.

\subsection{Officers}
The Davis CS Club Core Officers shall consist of the following:
\begin{enumerate}[a.]
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
\item President
\item Vice President (2)
\item Treasurer
\item Secretary
\item Webmaster
\item Public Relations
\item Events
\item Committee Chair(s) (As many as there are committees)
\end{enumerate}

\subsection{Eligibility Requirements}
At the beginning of each quarter, each Officer shall have up to two weeks to provide proof of fulfilling the following requirements:
\begin{li}
\item Be a current University of California, Davis student.
\item Maintain a cumulative 2.0 Grade Point Average (GPA).
\item Not be subject to Academic Disqualification (quantitative or qualitative) under the Office of the University Registrar.
\item Have attended at least three (3) full meetings and one (1) event in quarters prior to the election.
\end{li}

\subsection{Duties and Responsibilities}
Each Core Officer shall:
\begin{li}
\item Strive to always accurately and equally represent the desires and opinions of all members of the club to the best of their abilities in all their actions as a Core Officer.
\item Chair or Vice Chair one (1) Committee.
	\begin{li}
	\item If there are less Core Officers than there are Committees, each Core Officer may Chair or Vice Chair more than one (1) Committees to prevent suspension or dissolution of Committees.
	\item Each Officer chairing more than one (1) Committees must nominate a Core Member to a Chair or Vice Chair position to replace them within two (2) weeks. Otherwise, the committee shall be suspended until a Core Member can be nominated.
	\end{li}
\item Maintain a membership and attendance of Davis CS Club meetings, events, and at least one (1) Committee's meetings and events.
\item Participate and attend a minimum of two (2) events per quarter. Each Officer must check-in with an Officer that coordinated the event.
\item Maintain an online presence regarding the Davis CS Club. Online activities can include but is not limited to:
	\begin{itemize}
	  \setlength{\itemsep}{1pt}
	  \setlength{\parskip}{0pt}
	  \setlength{\parsep}{0pt}
	\item Contributing to the Davis CS Club Facebook Group.
	\item Contributing to the official email address for the Davis CS Club Officers.
	\end{itemize}
\item Submit and update a schedule that includes classes, other club or society meeting times, and work, internship, or research hours to the Vice President(s) by the the first week of every quarter, and update the Vice President(s) appropriately throughout the quarter.
\item Be familiar with the Davis CS Club fiscal matters.
\item Maintain and add to their collection of records, resources, and recommendations relating to their position, and ensure that it is passed on to the successors of respective Officer positions.
\item Submit a written business report of their respective Officer position to the Core Body and the Secretary at every regular Core Officer meeting.
\item Present the written business report of their respective Committees at every regular Core Officer meeting.
\item Perform all duties delegated to them by the Core Body and the Bylaws.
\end{li}

\subsection{Individual Duties and Responsibilities}
\begin{enumerate}[A.]
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
\item President\\
	The Davis CS Club President shall:
	\begin{li}
	\item Act as the main spokesperson for the Davis CS Club.
	\item Provide professionalism, leadership, direction, empowerment, and dedication for the Davis CS Club.
	\item Chair and facilitate the Davis CS Club General Meetings and the Executive Advisory Committee Meetings.
	\item Deliver an outline of the vision of the Davis CS Club to the Computer Science Department and the University community.
	\item Set the agenda of all Davis CS Club General Meetings.
	\item Swear in the Davis CS Club Officer elects.
	\item Be an authorized and required signer for the accounts assigned by the Budget Code.
	% \item Maintain a relationship with the Center for Student Involvement and register the club each year.
	% \item Check the club's mailboxes on a regular basis.
	\end{li}
\item Vice President of Internal Affairs\\
	The Davis CS Club Vice President of Internal Affairs shall:
	\begin{li}
	\item Assist the President in their duties.
	\item Serve as the Vice President of the Executive Advisory Committee.
	\item Recommend appointment and removal of members to Core Body as they see fit, with the approval by a majority vote of the Core Body.
	\item Maintain attendance records of all Core Officers.
	\item Collect, log, and file data on Officers' fulfillment of duties delegated by the Davis CS Club Bylaws.
	\item Review all written business reports with the Secretary before publishing them Online.
	\item Facilitate accountability for the Core Body and Committee Chairs.
	\end{li}
\item Vice President of External Affairs\\
	The Davis CS Club Vice President of External Affairs shall:
	\begin{li}
	\item Assist the President in their duties.
	\item Act as the second EJC (Engineering Joint Council) Representative, if necessary.
	\item Provide a welcoming and inclusive club environment, and encourage current and future members to attend meetings and events of the Davis CS Club.
	\item Work with the Events Officer to provide a marketing plan for publicity efforts of meetings and events of the Davis CS Club.
	\item Delegate tasks to the Core Body according to the marketing plan for meetings and events of the Davis CS Club.
	\item Coordinate with the Secretary and the Webmaster to maintain the membership database for meetings and events of the Davis CS Club.
	\item Maintain a relationship with the Club Advisor and the Major Advisor and regularly provide updates and receive feedback for the Davis CS Club.
	\item Work with the Public Relations Officer to maintain a professional, continuing relationship with organizations outside of the Davis CS Club.
	\item Overseer the Vice President of Internal Affairs in their duties.
	\end{li}
\item Treasurer\\
	The objectives of the Treasurer will be financial accountability with the following areas of focus:
	\begin{li}
	\item Be fully knowledgable about financial accounts and reserves, fiscal data, as well as sponsorships, grants, scholarships, and other funding available for the Davis CS Club.
	\item Ensure that all financial activities of the Davis CS Club legally comply with all Federal, State, and Local laws, District rules, and rules under the College of Letters and Sciences and the College of Engineering.
	\item Overseer all financial accounts and reserves belonging to the Davis CS Club.
	\item Audit and evaluate programs funded or Committees requesting funding from the Davis CS Club, and recommend requests for funding to the Core Body.
	\item Collect all fiscal data and maintain a database of financial records for the Core Body.
	\item Recommend monthly and/or quarterly financial analysis and budget planning in accordance with Actions to the Core Body.
	\end{li}

	\noindent The Core Body delegates authority to the Executive Advisory Committee to take action on behalf of the Treasurer to fulfill its own objectives with the following restrictions:
	\begin{li}
	\item Funding must be approved by the Core Body.
	\item Amending or allowing special exceptions for budget stipulations must be approved by the Core Body.
	\end{li}
\item Secretary\\
	The intended purpose of the position of Secretary shall be:
	\begin{li}
	\item To record the Actions of the Core Body at every Core Officer Meeting and to make such records accessible to all interested parties.
	\item To collect the records of every Committee Meeting from Committee Vice Chairs and to make such records accessible to all interested parties.
	\item To recommend or to appoint another Core Officer to record General Meetings.
	\item To maintain a database of all records required by the Davis CS Club bylaws.
	\item To communicate with the Vice President(s) and the Webmaster to organize all data and submit them for an Online public record.
	\item To schedule and publicize every Meetings required by the Davis CS Club bylaws.
	\end{li}
\item Webmaster\\
	The Webmaster shall:
	\begin{li}
	\item Represent the Davis CS Club and its written Purpose as provided by the Bylaws as a professional Online persona.
	\item Maintain and update the Davis CS Club Website at least once a week.
	\item Maintain and update a Wiki for the Davis CS Club regularly.
	\item Submit written reports summarizing amendments to the website, to the Core Body.
	\item Create and chair a Committee dedicated to managing the website, if necessary.
	\end{li}
\item Public Relations
	\begin{li}
	\item Act as the EJC (Engineering Joint Council) Representative.
	\item Maintain a relationship with other clubs outside of EJC meetings.
	\item Collect, empower, and engage volunteers that will participate in Committee Meetings and Events in a conducive manner.
	\item Manage the Officers' email address if necessary and act as a liaison between companies and the President.
	\item Remain in constant, professional communication with companies, sponsors, and other organizations in collaboration with the Davis CS Club.
	\end{li}
\item Events\\
An event shall be defined as a convening of Core members for an Action fulfilling the purposes of the Davis CS Club.
	\begin{li}
	\item Collaborate with the Core Body in organizing all future events.
	\item Act as a liaison or delegate another member in reserving rooms for all events of the Davis CS Club.
	\item Organize a Welcome event for Fall Quarter.
	\item Organize a Classes Meeting every Quarter.
	\item Organize an Introductory Overview Event in preparation for elections for late Winter or early Spring Quarter.
	\item Organize at least one (1) event every Quarter in collaboration with other organizations on campus.
	\item Devise an outreach plan for every major Action for the Davis CS Club.
	\item Provide and submit an analysis of results for every major event held to the Core Body and the Secretary.
	\item Provide a public Events Calendar for the Davis CS Club, which must be updated a week before the month starts, every month.
	\item Maintain the equipment and technological resources of the Davis CS Club.
	\end{li}
\item Committees Chair(s) (As many as there are committees)\\
	Each Committee Chair shall:
	\begin{li}
	\item Chair and facilitate their respective Committee meetings.
	\item Schedule and set the agendas of all meetings of their respective Committees.
	\item Appoint a Vice Chair to their respective Committee.
	\item Instruct their respective Committee Vice Chair on the duties to be performed in the Chair's absence.
	\item Recommend appointment and removal of members to their respective Committees as they see fit, with the approval by a majority vote of the Core Body.
	\end{li}

\noindent Each Committee Vice Chair shall:
\begin{li}
\item Assume the duties of their respective Committee Chair when he/she is absent or unavailable.
\item Ensure proper meeting minutes are recorded for the Core Body.
\item Provide all Committee Meeting Minutes to the Core Body and the Secretary.
\end{li}

\end{enumerate}

\subsection{Terms of Office}
A term shall be defined as one (1) academic year.
\begin{li}
\item Holding office for any portion(s) of a term shall count as holding office for one (1) term.
\item All Officers may hold office for a total of three (3) consecutive or non-consecutive terms.
\item All Officers shall be elected and sworn in the third week of every Spring Quarter.
\item All newly elected Officers must shadow the previous Officers for the remainder of the quarter.
\item After the last week of Spring Quarter, the new Officers shall immediately assume their elected positions.
\item All Officers shall continue to hold office until newly elected Officers are sworn in.
\end{li}

\subsection{Succession of Officers}
For times at which the President and the Vice President(s) are temporarily unable to perform their respective duties, the order of succession of their responsibilities shall be as follows:
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
\item Secretary
\item Public Relations
\item Treasurer
\item Events
\item Committee Chairs
\end{itemize}
In any event where a Committee Chair is temporarily unable or unavailable to perform their duties, the respective Committee Vice Chair shall succeed the duties of their Committee Chair.\\

\noindent The succession of officers shall not represent the hierarchy of the organization.

\subsection{Resignation}
\begin{li}
\item Any Officer may resign from their position at any time by submitting a resignation in writing to any Core Officers.
\item Verbal resignations shall be considered official and binding only when made at a Davis CS Club Meeting.
\item Resignations are immediately effective unless a date is otherwise specified.
\end{li}

% ////////////////////////////////////////////////
% ////////////////////////////////////////////////

\section{Committees}
\subsection{Club Committees}
The Davis CS Club Committees shall include but not be limited to the following:
\begin{li}
\item Executive Advisory Committee
\item Website Development Committee
\item Mock Interview Committee
\item Tutoring Committee
\end{li}
\subsection{Formation and Dissolution}
\begin{li}
\item Each Committee shall be formed by a majority vote of the Core Body.
\item All Committees must be formed with the following definitions:
	\begin{li}
	\item Name of the body.
	\item Purpose of the body.
	\item Authority of the committee to take action on behalf of the Core Body under specific circumstances.
	\item A document (Committee Code) briefly outlining information regarding Membership, Duties and Responsibilities, Chairs and Vice Chairs, and other Special Memberships.
	\end{li}
\item If at any time a Committee does not fulfill its minimum membership as specified in the respective Committee Code, then that body automatically becomes inactive and must meet its minimum membership to resume its duties.
	\begin{li}
	\item The duties and responsibilities during such time are to be assumed by the Executive Advisory Committee.
	\end{li}
\end{li}

\subsection{Duties and Responsibilities}
Each Committee shall:
\begin{li}
\item Conduct its business in accordance with its Committee Code
\item Hold Committee Meetings in accordance with these Bylaws.
\item Work on business referred to it by the Core Body.
\item Review its Committee Code at least once, and submit any proposed amendments to the Executive Advisory Committee.
\end{li}

% Pillars are informal guideline and not official

\subsection{Executive Advisory Committee}
The objectives of the Executive Advisory Committee is to provide leadership to the Core Body through the following:
\begin{li}
\item Maintain the ability of the Core Body to perform work for the Davis CS Club.
\item Maintain documents and forms of the Core Body.
\item Offer training to all members of the Core Body in regards to professionalism or developing leadership, as well as the position of the Core Body in the organizational structure of the College of Letters and Sciences and the College of Engineering.
\item Create and prioritize a set of goals for the Core Body, and amend such goals as necessary.
\item Ensure that goals are being accomplished by assisting individuals and/or Committees.
\item Author policies and procedures that are necessary but are not specifically addressed by these Bylaws nor any codes adopted by the Core Body, and forward such documents to the Core Body for approval.
\end{li}

\noindent The membership of the Executive Advisory Committee shall be:
\begin{li}
\item President
\item Vice President (s)
\end{li}

\noindent The Core Body delegates authority to the Executive Advisory Committee to propose agenda items for Core Officer Meetings or to take action on behalf of the Core Body to fulfill its own objectives with the following restrictions:
\begin{li}
\item Any agenda items not outlined by Article I, Section ii of these Bylaws may not be introduced, unless originally referred to this Committee by the Core Body.
\item Any project to implement new technology or equipment must be approved by the Core Body prior to beginning the project.
\item Any amendments to Bylaws or Codes must follow procedures outlined in these Bylaws and be approved by the Core Body.
\end{li}

% \subsection{Professional Development Committee}
% The objective of the Professional Development Committee is the preparation of Core Members to leave a professional impression at future interviews, events, or other meetings with employers, Universities or Colleges, or professional agencies. The Professional Development Committee must:
% \begin{li}
% \item Work with the Events Officer and overseer all events to ensure professionalism.
% \item Plan at least one (1) event per year for an event with a completely professional setting in coordination with one (1) other of the three pillars.
% \end{li}

% \noindent The Core Body delegates authority to the Executive Advisory Committee to take action on behalf of the Professional Development Committe to fulfill its own objectives.

% \subsection{Distinguished Speakers Committee}
% The objective of the Distinguished Speakers Committee is the provision of 

% \subsection{Website Development Committee}
% The objective of the Website Development Committee is to provide the Core Members an opportunity to join a community project that will contribute to the Davis CS Club as well as their skillset and 

% \subsection{Mock Interview Committee}
% The objective of the Mock Interview Committee is

% \subsection{Tutoring Committee}
% The objective of the Tutoring Committee is 

% ////////////////////////////////////////////////
% ////////////////////////////////////////////////

\section{Meetings}
\subsection{General Meetings}
The Davis CS Club shall conduct regular, open general meetings on every Wednesday, excluding during break, first week, dead day, and finals week, with each meeting convening at 5:30 PM and adjourning after 6:00 PM.

\subsection{Core Body Meetings}
The Core Body shall conduct regular Core Officer Meetings on every Monday, excluding during break, first week, dead day, and finals week, with each meeting convening at 5:30 PM and adjourning after 6:00 PM.

\subsection{Internal Committee Meetings}
The Committees shall conduct regular Internal Committee Meetings at least two (2) times per month as deemed necessary by the respective Chair, excluding during break, first week, dead day, and finals week.

% Change to percentage based on current members when low number of members 

\subsection{Quorum}
A quorum must be necessary for continuing any Core Officer meeting or Internal Committee Meetings.
\begin{li}
\item Establishment of Quorum
	\begin{li}
	\item Quorum for Core Body shall be established when no less than fifty-percent (50\%) plus one of the respective members are present.
	\end{li}
\item The Core Body and Committees shall not take any official vote upon, or take any official action regarding any issue at any of their meetings when quorum is not in effect.
	\begin{li}
	\item At the discretion of those Officers in attendance, the Core Body or Committee shall be permitted to take official votes and actions on an emergency basis when quorum is not in effect, but if not subsequently ratified at a meeting of that body with quorum, all such actions shall be considered null and void.
	\end{li}
\end{li}

% ////////////////////////////////////////////////
% ////////////////////////////////////////////////

\section{Elections}
\subsection{General Election}
\begin{li}
\item The Davis CS Club general election shall be conducted in accordance with Article III, section v of the Davis CS Club Bylaws.
\item The President shall chair the first meeting of each Committee Meeting with the only business to be selecting the Committee Chair and Committee Vice Chair.
\end{li}
\subsection{Filling Vacant Positions}
\begin{li}
\item Vacancy of the President shall automatically be filled by the Vice President(s) which is effective immediately. In the case of two Vice Presidents, one Vice President will fill the vacancy with a majority approval of the Core Body.
\item Vacancy of the Vice President position(s) shall be filled by a recommendation by the President which must receive majority approval by the Core Body before becoming effective.
\item In the event that the positions of the President and both Vice Presidents become vacant, the Secretary shall conduct an internal election to fill the positions.
\item In the event there is a vacancy in any Chair position, the Vice Chair of the respective Committee shall succeed to that position after confirmation by a majority vote of the Core Body.
\item Once an Officer is elected, they shall immediately assume all the duties and responsibilities of their position.
\item If an Officer succeeds to another Officer position, then they are assumed to resign all other positions.
\end{li}

% ////////////////////////////////////////////////
% ////////////////////////////////////////////////

\section{Removals}
\subsection{Automatic Removal}
\begin{li}
\item When an Officer fails to meet their eligibility requirements, they shall be removed from their position.
\item When an Officer has missed three (3) Core Officer Meetings, they shall automatically be removed from their position.
	\begin{li}
	\item The person removed may appeal to the Core Body. If they receive a super-majority (2/3) vote to approve the appeal, then they shall be reinstated as their original position.
	\item The appeal must be done within two (2) Core Officer Meetings.
	\item There may only be one (1) appeal opportunity per term for each Officer. The Vice President(s) will notify the Core Body in cases of automatic removal with a 'Non-action Business' agenda item.
	\end{li}
\end{li}
\subsection{Officer Removal}
\begin{li}
\item Any five (5) Officers may submit a Officer Removal Request to the Core Body at any time calling for the removal of an Officer from their position.
\item The Peer Removal Request must cite the section(s) of the Davis CS Club Bylaws that have been violated by the Officer in question.
\item The Vice President(s) shall notify the Officer in question of their right to appear at the removal proceeding, which shall be at the next Core Officer Meeting.
	\begin{li}
	\item If the Vice President is in question, the President shall notify the Officer in question of their right to appear at the removal proceeding.
	\end{li}
\item The Vice President(s) shall place the removal proceeding on the Core Officer Meeting agenda and present the Officer's case to the Core Body.
	\begin{li}
	\item If the Vice President is in question, the President shall present the case to the Core Body.
	\end{li}
\item The Core Body shall debate the act of removing the Officer in question, from which the Officer in question cannot be excluded.
	\begin{li}
	\item The debate must include one argument for and one argument against before the debate may end.
	\item The Officer in question must be afforded two (2) minutes to speak.
	\end{li}
\item The Officer may be removed with the approval by a super-majority (2/3) vote of the Core Body. The Officer in question may vote on this matter.
\item The Officer removed from office shall be allowed one (1) appeal within two (2) Core Officer Meetings of their removal.
\end{li}

\subsection{Removal by Members}
The Core Members shall be permitted to seek to directly discipline or remove any Officer by submitting a petition to the Club Advisor signed by at least fifty (50) percent of the Core Members. The petition must include the following:
\begin{li}
\item Description of the manner in which the Officer in question has failed to fulfill their duties.
\item Request of disciplinary action and/or removal of that Officer.
\item Each signer's full printed name, signature, and student ID number.
\end{li}

% ////////////////////////////////////////////////
% ////////////////////////////////////////////////

\section{Sponsorship}

% ////////////////////////////////////////////////
% ////////////////////////////////////////////////

\section{Amendment and Adoption}
All amendments to the Davis CS Club Bylaws and Committee Codes must follow this process:
\begin{li}
\item An Officer or a Committee shall propose amendments to the Davis CS Club Bylaws and Committee Codes.
\item All proposed amendments to the Committee Codes must be referred to the respective Committees for approval.
\item Each Committee may approve, approve as amended, or reject the proposed amendments.
\item For Committee Code amendments, the Core Body may only consider amendments approved or approved as amended by the respective Committees.
\item The amendment shall appear as a business item on the Core Officer Meeting agenda no less than one (1) week from submission. A discussion must take place before any adoption, amendments, or rejection of amendments.
\item All amendments shall require an approval by a two-thirds (2/3) vote of the Core Body.
\item Amendments must be published at least one week before the general meeting in which it will be ratified.
\item Minor amendments such as typos or grammatical errors may be approved and ratified without the approval of the Davis CS Club.
\item The amendment approved must be published in documents available online.
\end{li}

% ////////////////////////////////////////////////
% ////////////////////////////////////////////////

\section{History}
\subsection*{Version 0}
January 1, 2013.\\
Current Status: Not submitted. Unapproved by Core Body. Unadopted by the Davis CS Club.
\subsection*{Version 0.1}
January 13, 2013.\\
Current Status: Submitted. Approved by Core Body. Unadopted by Davis CS Club.
\subsection*{Version 0.2}
January 16, 2013.\\
Current Status: Submitted. Approved by Core Body. Unadopted by Davis CS Club.
\subsection*{Version 1}
April 9, 2014.\\
Current Status: Submitted. Approved by Core Body. Adopted by Davis CS Club.

\end{document}